### 2016-07-22 doc/publications/plos16/plos16.tex
remove seconds

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
\hline

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364} & CursedForest & XX & 1hr 58min 23sec & 4GB \\
& RF (Spark ML) & 0.94 & 8hr 29min 07sec & 8GB \\
& LR &  & 10hr 30min & 8GB\\ \hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051}  & CursedForest & &  &\\
& RF(Spark ML) & &  &\\
& LR & &  &\\ \hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & CursedForest & 0.96 & 7hr 14min 40sec & 8GB \\ 
& RF (Spark ML) & - & - & - \\
& LR & - & - & - \\ 
& kmeans (Spark ML) & 0.82 & 30hr 44min 00sec & 24GB \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project. Size of the data is individuals x variants

>>>>

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{Method} & \bf{Accuracy} & \bf{Runtime} & \bf{Memory/Node} \\
\hline

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364} & CursedForest & XX & 1hr 58min & 4GB \\
& RF (Spark ML) & 0.94 & 8hr 29min & 8GB \\
& LR &  & 2hr 6min & 8GB\\ \hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051}  & CursedForest & 0.046 () & 4hr 0min & 4GB\\
& RF(Spark ML) & &  &\\
& LR & & 14hr 48min & 8GB \\ \hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & CursedForest & 0.96 & 7hr 14min & 8GB \\ 
& RF (Spark ML) & - & - & - \\
& LR & - & - & - \\ 
& kmeans (Spark ML) & 0.82 & 30hr 44min & 24GB \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project. Size of the data is individuals x variants
